---
title: "Manatees, using rOpenSci"
author: "Jacquelyn Neal"
date: "April 21, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(rgbif)
library(mapr)
library(spocc)
library(ggplot2)
```

```{r,fig.height=8,fig.width=12,warning=FALSE,message=FALSE,include=FALSE}
# First we need species key for manatee species
key <- name_suggest(q='Trichechus manatus', rank='species')$key[1]
dat <- occ_search(taxonKey=key,return='data')

out <- occ(query = 'Trichechus manatus', from = 'gbif', has_coords = TRUE)
map_plot(out)
```
### Background
I was born and raised in Southwest Florida, as a fourth-generation Floridian, and was lucky to have an amazing environmental education. After years of obsession with Florida's poster mammal, I had the opportunity to visit Crystal River and Homosassa Springs to snorkel with manatees twice while in middle school. So when I started learning the rgbif package, I decided to examine data on the mammal I've grown up studying.

There are three living species of manatee: Trichechus inunguis (Amazonian), Trichechus manatus (West Indian), and Trichechus senegalensis (West African). Not much is known about the Amazonian and West African manatees, but they are hypothesized to be similar to the West Indian species.

### R Packages to Use
```{r, include=TRUE}
library(rgbif)
library(mapr)
library(spocc)
library(ggplot2)
```

### Manatee Data
```{r,fig.height=8,fig.width=12,warning=FALSE,message=FALSE}
splist <- c('Trichechus inunguis', 'Trichechus manatus', 'Trichechus senegalensis')
keys <- sapply(splist, function(x) name_suggest(x)$key[1], USE.NAMES=FALSE)
dat <- occ_search(taxonKey=keys, return='data', limit=300)
```

### Using map_plot
```{r first map,fig.height=8,fig.width=12,warning=FALSE,message=FALSE}

out <- occ(query = splist, from = 'gbif', has_coords = TRUE)
map_plot(out)
```

### Using map_ggplot
```{r,fig.height=8,fig.width=12,warning=FALSE,message=FALSE}
map_ggplot(out) + ggtitle("Sightings of Manatee Subspecies")
```

### Using map_ggmap
```{r,fig.height=8,fig.width=12,warning=FALSE,message=FALSE}
map_ggmap(out,zoom=2) + ggtitle("Sightings of Manatee Subspecies")

```

